Rotations and Insecticide Resistance initial plots

### 2017-10-31 inst/documents/rotations_notes.Rmd
get UI to cope with split dominance

I'm nervous about making the rotation repsonsive. We both said that i unlikely to happen in the field.

@@

*11/10/17*

@@

~ set dominance of cost and dominance of selection to be different in fitness_single_locus().

@@

# state of play
~ rotations1.Rmd : example plots

>>>>

I'm nervous about making the rotation responsive. We both said that i unlikely to happen in the field.

@@

~ setting dominance of cost and dominance of selection to be different in fitness_single_locus().

*31/10/17*

UI :
Warning: Error in run_rot: argument 6 matches multiple formal arguments

probably due to recent splitting of dominance

Yes, fixed now.

Increasing dominance of cost decreases resistance, 
increasing dominance of selection increases resistance. (both as expected)

@@

@@

# state of play
~ rotations1.Rmd : example plots
~ UI : rotations/shiny/rotresist1/server.r

# funding opportunities
https://lstmed.sharepoint.com/research/RBPS/Pages/Funding%20Information/Funding-Opportunities.aspx     
https://www.researchprofessional.com/funding/simple?q=software#1509451534514
